Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-01 Draft/Draft.Rmd
some edits

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are cosidered the building blocks that depict subsets of interactions of the network. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions of plant-pollinator networks in natural systems.

Motifs are abstract representations often decoupled from species ecology.

[explain here the importance of relating reproductive strategies and pollinators behaviours to their positions within a motif. This is interesting because bridges pairwise interactions to the emergent network via motifs]

@@

plant functional groups by using a comprehensive dataset with several reproductive traits and pollinator functional groups as the main differentiated guilds in life form and behaviour. Then, we explored the main motifs of these networks and we found [...]

>>>>

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are cosidered the building blocks that depict subsets of interactions of the network. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Although past studies have evaluated the ecological implications of motifs [@stouffer2012; @simmons2019], motifs are abstract representations often decoupled from species ecology. Species with different reproductive strategies may occupy different positions and be represented in different motifs. At the micro-scale, @tur2013 have linked the degree of pollinator dependence with specialization. However, meso-scale studies have not evaluated the implications and potential of considering the species reproductive strategy.

@@
